### 2025-07-08 index.qmd
20250707 - additional resources
20250707 - PCA fixes and citations

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "broom", "broom.mixed", 
  "downlit", "xml2", "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", 
  "patchwork", "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", 
  "sjstats", "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", 
  "fitdistrplus", "sn", "mclust", "magrittr", "viridis", "plotly", "quantmod", 
  "fPortfolio", "NMOF", "xts", "zoo", "forecast", "stringi", "parallel", #"webshot2"
  "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin", "caret", 
  "tidymodels", "LongituRF", "gpboost", "cmdstanr", "learnr", "remotes", 
  "corrplot", "correlation", "mgcv", "rms", "car", "performance", "lavaan", 
  "mice", "miceadds", "interactions", "shiny", "PearsonDS", "robustbase", 
  "ordinal", "MASS", "data.table", "future", "future.apply", "QuantPsyc", 
  "SimDesign", "effectsize"
)

@@

>>>>

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "broom", "broom.mixed", 
  "downlit", "xml2", "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", 
  "gsisdecoder", "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", 
  "dagitty", "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", 
  "patchwork", "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", 
  "sjstats", "AICcmodavg", "rstan", "brms", "tidybayes", "bbmle", 
  "fitdistrplus", "sn", "mclust", "magrittr", "viridis", "plotly", "quantmod", 
  "fPortfolio", "NMOF", "nFactors", "xts", "zoo", "forecast", "stringi", #"webshot2"
  "parallel", "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin", 
  "caret", "tidymodels", "LongituRF", "gpboost", "cmdstanr", "learnr", 
  "remotes", "corrplot", "correlation", "mgcv", "rms", "car", "performance", 
  "lavaan", "mice", "miceadds", "interactions", "shiny", "PearsonDS", 
  "robustbase", "ordinal", "MASS", "data.table", "future", "future.apply", 
  "QuantPsyc", "SimDesign", "effectsize"
)

@@

## Example Syllabus {#sec-exampleSyllabus}

If you are interested in teaching a course using this textbook, here is an example syllabus based on my class: <https://isaactpetersen.github.io/psy-3170-2025-fall/syllabus.html>

### 2025-07-08 pca.qmd
20250707 - PCA fixes and citations

@@

@@

```{r}
psych::vss(
  dataForPCA[pcaVars],
  rotate = "oblimin",
  fm = "pc")
```

>>>>

We generated the scree plot in @fig-pcaScreePlot1 using the `fa.parallel()` function of the `psych` package [@R-psych].

@@

We generated the scree plot in @fig-pcaScreePlot2 using the `nScree()` and `plotnScree()` functions of the `nFactors` package [@R-nFactors].

@@

We generated the very simple structure (VSS) plot in @fig-pcaVSSPlot using the `vss()` function of the `psych` package [@R-psych].

```{r}
#| label: fig-pcaVSSPlot
#| fig-cap: "Very Simple Structure Plot."
#| fig-alt: "Very Simple Structure Plot."

psych::vss(
  dataForPCA[pcaVars],
  rotate = "oblimin",
  fm = "pc")
```
